### 2021-07-11 doc/thesis/chapters/dsp.tex
add list of abbrev
structuring

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Receiver types}

@@

\subsection{Mathematical description}

@@

\section{Sampling theorem}

@@

This chaper describes the main properties of broadcast FM, such as the mathematical description, frequency bands that are used, or the specific frequency parts within a channel spectrum.

@@

This chapter describes the demodulation of the information content of an FM broadcast channel, as it is used in commercial FM radio broadcasting.
The assumption here is, that the actual FM demodulation, as described in chapter \ref{sec:algorithms-for-digital-fm-demodulation} is already done correctly.
A frequency spectrum of the multiplex signal of an FM channel is shown in Fig.\ref{fig:fm_channel_baseband_freqs}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Receiver Types}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mathematical Description}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sampling Theorem}

@@

This section describes the main properties of broadcast FM, such as the mathematical description, frequency bands that are used, or the specific frequency parts within a channel spectrum.

@@

This section describes the demodulation of the information content of an FM broadcast channel, as it is used in commercial FM radio broadcasting.
The assumption here is, that the actual FM demodulation, as described in chapter \ref{sec:algorithms-for-digital-fm-demodulation} is already done correctly.
A frequency spectrum of the multiplex signal of an FM channel is shown in Fig.\ref{fig:fm_channel_baseband_freqs}.

### 2021-07-11 doc/thesis/chapters/implementation.tex
\includepicture function with floating option; new block diagram
structuring

%%%%%%%%%%%%%%%%%%%%
\chapter{Implementation}
\label{cha:Implementation}
\section{Matlab/Python Model}
  in fixed point, close to hardware level algorithm

  \section{VHDL (no shortcut)}
  \subsection{Channel Selection (IF to Channel-BB)}
  \subsection{Phase Detector}
  \subsection{other Elements}

  \section{High-Level Synthesis}
  \subsection{Channel Selection (IF to Channel-BB)}
  \subsection{Phase Detector}
  \subsection{other Elements}

@@

  \section{Develop HLS compiler independent code (optional)}
  \subsection{Challenges}
  Different compilers use different \#pragmas, etc.\\
  The \#pragmas need to be within the code, at the appropriate positions, which makes it difficult to write compiler independent code....

>>>>

%%%%%%%%%%%%%%%%%%%%
\chapter{Implementation}
\label{cha:Implementation}

This chapter describes the most important details of each implementation variant.

\section{Digital Signal Processing Chain}

\includepicture [1.0] {Detailed block diagram of the digital signal processing chain.} {bd_dsp_detailed} {img/bd_detailed_dsp}

\section{Matlab Model}

in fixed point, close to hardware level algorithm

\subsection{Transmitter block diagram}

\section{GNU Radio}
  \subsection{Introduction}
  \subsection{Transmitter}
  \subsection{Receiver}

\section{VHDL (no shortcut)}
  \subsection{Testbench}
  \subsection{Channel Selection (IF to Channel-BB)}
  \subsection{Phase Detector}
  \subsection{other Elements}

  \section{High-Level Synthesis}
  \subsection{Testbench}
  \subsection{Channel Selection (IF to Channel-BB)}
  \subsection{Phase Detector}
  \subsection{other Elements}

@@
